\cvsection{Experience}





\begin{cventries}
  \cventry
    {PHD Candidate / Teaching Assistant} % Job title
    {Heriot-Watt University} % Organization
    {Edinburgh, UK} % Location
    {Oct 2019 - Jan 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching assistant and lab demonstrator of Data Communications and Networking}
		\item {Teaching assistant and lab demonstrator of Computer Network Security}
		 \item {Teaching assistant and lab demonstrator of Advanced Network Security}
		\item {Teaching assistant and lab demonstrator of Software Development 1(Java)}
      \end{cvitems}
    }


  \cventry
    {Research Intern} % Job title
    {Huawei UK Edinburgh R\&D} % Organization
    {Edinburgh, UK} % Location
    {Feb 2022  - Aug 2022 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creating solutions to indoor positioning problems with machine learning methods}
		\item {Distance estimating using WiFi fingerprinting}
		 \item {Community detection using WiFi distances}
		%\item {}
      \end{cvitems}
    }
  \cventry
    {Teacher Trainer} % Job title
    {Turkish Ministry of National Education} % Organization
    {Manisa, Turkey} % Location
    {Sept. 2013 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
               \item {Teaching teachers how to use interactive board and board software and practicing the use of materials.}
\item {Teaching teachers about using online/offline software, electronic materials and applications in their field.}
\item {Teaching teachers about network technologies and network security issues.}
      \end{cvitems}
    }





  \cventry
    {Computer Teacher and Technology Consultant} % Job title
    {Turkish Ministry of National Education} % Organization
    {Manisa, Turkey} % Location
    {Sept. 2009 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing and implementing an effective computer-based curriculum.}
\item {Assigning, assisting, and grading students on computer projects.}
\item {Monitoring, assessing, and documenting student progress.}
\item {Teaching computer fundamentals and programming language to students.}\end{cvitems}}\end{cventries}
