%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}



%-------------------------------------------------------------------------------
\begin{cvhonors}
  \cvhonor
    {Semantic Verbal Fluency in Native Speakers of Turkish: A Systematic Review of Category Use, Scoring Metrics and Normative Data in Healthy Individuals.} % Award
    {Rabia Yasa Kostas, \textbf{Kahraman Kostas}, Sarah E. MacPherson, and Maria K. Wolters.  Journal of Clinical and Experimental Neuropsychology.} % Event
    {Q2} % Location
    {Under Review} % Date(s)

  \cvhonor
    {IoTGeM: Generalisable Models for Behaviour-Based IoT Attack Detection.} % Award
    {\textbf{Kahraman Kostas}, Mike Just, and Michael A. Lones. IEEE Transactions on Dependable and Secure Computing. \href{https://github.com/kahramankostas/IoTGeM}{\faGithub}~\href{https://github.com/kahramankostas/IoTGeM/blob/main/IoTGeM-Generalisable-Models-for-Behaviour-Based-IoT-Attack-Detection.pdf}{\faExternalLink}} % Event
    {Q1} % Location
    {Under Review} % Date(s)



%---------------------------------------------------------

  \cvhonor
    {IoTDevID: A behavior-based device identification method for the IoT} % Award
    {\textbf{Kahraman Kostas}, Mike Just, and Michael A. Lones.  IEEE Internet of Things Journal 9.23 (2022): 23741-23749. \href{https://github.com/kahramankostas/IoTDevIDv2}{\faGithub}~\href{https://ieeexplore.ieee.org/document/9832419}{\faExternalLink} } % Event
    {Q1} % Location
    {2022} % Date(s)

  \cvhonor
    {WiFi Based Distance Estimation Using Supervised Machine Learning.} % Award
    {\textbf{Kahraman Kostas}, Rabia Yasa Kostas, Francisco Zampella; Firas Alsehly.  2022 IEEE 12th International Conference on Indoor Positioning and Indoor Navigation (IPIN). IEEE.\href{https://github.com/kahramankostas/WiFi-Fingerprint}{\faGithub}~\href{https://ieeexplore.ieee.org/document/9918128}{\faExternalLink} } % Event
    {-} % Location
    {2022} % Date(s)
    
    
 


%---------------------------------------------------------
\end{cvhonors}